### 2015-04-21 paper.tex
Define MHK

\section*{Introduction}
Sandia National Laboratory (SNL) developed the cross-flow turbine, Reference
Model 2 (RM2), to provide an open-source point design for MHK research and
development, including its use as a test object for scaled model testing to
generate power performance data that can be used to validate open-source design
tools. More details on the reference modeling effort are provided in Neary et
al. \cite{Neary2014}.

>>>>

\section*{Introduction} Sandia National Laboratory (SNL) developed the
cross-flow turbine, Reference Model 2 (RM2), to provide an open-source point
design for marine hydrokinetic (MHK) energy research and development, including
its use as a test object for scaled model testing to generate power performance
data that can be used to validate open-source design tools. More details on the
reference modeling effort are provided in Neary et al. \cite{Neary2014}.
